R Markdown for Reproducible Research

### 2019-01-07 paper.Rmd
finish up section on r notebooks

```
---
title: "R Markdown for Reproducible Research"
output: pdf_document
---
```

@@

@@

>>>>

```yaml
---
title: "R Markdown for Reproducible Research"
output: pdf_document
---
```

@@

The most noteworthy difference about R Notebooks versus plain R Markdown is that
they are somewhat _stateful_. This means that they cache and display output as
it is generated, making it easier to interactively and iteratively build a
narrative without having to re-render the document each time you have made a
change.

It is worth noting that this output can be **problematic for reproducibility**,
though, since you may have unknowingly persisted an output (state) that is no
longer relevant or reproducible.

As a result, R Notebooks can be thought about as good for interactive
exploration or discussion among developers, but moving to an R Markdown format
is generally preferred once the report has stabilized or is being shared with an
end user.

R Notebooks are identified by `output_type: html_notebook`. Remember that you can have
multiple output types, so a YAML header like the following allows you to easily
build multiple output types from the same document.

```yaml
---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  pdf_document: default
  html_notebook: default
---
```

@@

Now that we have thoroughly explored the what of R Markdown, let us
now delve into _why_ this tool is useful for researchers.
